Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
modified pointers to min and max

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% inRange for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n}\mapsto\texttt{t} \ \ast \ \texttt{pn->n}\mapsto\texttt{min} \ \ast \  \texttt{pn->n}\mapsto\texttt{max} 
			\end{array}
			\right\}
		}
		\\ 
		\texttt{inRange(pn, k)} 
		\\
		{\color{blue}
			\left\{\mathit{res.} \
			\begin{array}{l}
				\texttt{pn->n}\mapsto\texttt{t} \ \ast \ \texttt{pn->n}\mapsto\texttt{min} \ \ast \  \texttt{pn->n}\mapsto\texttt{max} \  \ast  \ 
				\\(\mathsf{if}\ \mathit{res}\ \mathsf{then}\ (\texttt{min} < \texttt{k} < \texttt{max})\ \mathsf{else}\ (\texttt{k} \leq \texttt{min} \lor \texttt{k} \geq \texttt{max}))
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specification of \texttt{inRange} for the give-up template}
	\label{fig:inRange_giveup}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{\textwidth}
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\ \texttt{pn->n} \mapsto \texttt{NULL}  
			\end{array}
			\right\}
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\{\exists \  \texttt{t l r lk1 lk2}.
			\begin{array}{c}
				\ \texttt{pn->n->t} \mapsto \texttt{(k, v, l, r)} \ \ast \ \\ 
				\ \texttt{l} \mapsto \texttt{(NULL, lk1)}\  \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2)}
			\end{array}
			\right\}
		}
		\end{mathpar}
		\caption{Specification of \texttt{insertOp} for the lock-coupling template}
			\label{fig:insertOp_lock}
	\end{subfigure}
	%insertOp for give-up of give-up
	\begin{subfigure}{\textwidth}
		\begin{mathpar}
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n}\mapsto \texttt{NULL} \  \ast \ \texttt{pn->n}\mapsto \texttt{min} \ \ast \ \texttt{pn->n}\mapsto\texttt{max}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
		\left\{\exists \ \texttt{t l r lk1 lk2}. 
		\begin{array}{c}
			\texttt{pn->n->t}\mapsto \texttt{(k, v, l, r)} \  \ast \ \texttt{pn->n}\mapsto \texttt{min} \ \ast \ \texttt{pn->n}\mapsto\texttt{max}  \ \ast \ 
			\\ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, k))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (k, max))}
		\end{array}
		\right\}
	}
	\end{mathpar}
	\caption{Specification of \texttt{insertOp} for the give-up template}
	\label{fig:insertOp_giveup}
\end{subfigure}
	\caption{Specification of \texttt{insertOp} for the lock-coupling and give-up templates}
	\label{fig:insertOp}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% inRange for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n->min}\mapsto \mathsf{n_1} \ \ast \ \texttt{pn->n->max}\mapsto\mathsf{n_2}  
			\end{array}
			\right\}
		}
		\\ 
		\texttt{inRange(pn, k)} 
		\\
		{\color{blue}
			\left\{\mathit{res.} \
			\begin{array}{l}
				\texttt{pn->n->min}\mapsto \mathsf{n_1} \ \ast \ \texttt{pn->n->max}\mapsto\mathsf{n_2} \ \ast  \ 
				\\(\mathsf{if}\ \mathit{res}\ \mathsf{then}\ (\mathsf{n_1} < \texttt{k} < \mathsf{n_2})\ \mathsf{else}\ (\texttt{k} \leq \mathsf{n_1} \lor \texttt{k} \geq \mathsf{n_2}))
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specification of \texttt{inRange} for the give-up template}
	\label{fig:inRange_giveup}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{\textwidth}
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\ \texttt{pn->n} \mapsto \texttt{NULL}  
			\end{array}
			\right\}
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\{\exists \  \texttt{l r lk1 lk2}.
			\begin{array}{l}
				\ \texttt{pn->n->t} \mapsto \texttt{(k, v, l, r)} \ \ast \ \\ 
				\ \texttt{l} \mapsto \texttt{(NULL, lk1)}\  \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2)}
			\end{array}
			\right\}
		}
		\end{mathpar}
		\caption{Specification of \texttt{insertOp} for the lock-coupling template}
			\label{fig:insertOp_lock}
	\end{subfigure}
	%insertOp for give-up of give-up
	\begin{subfigure}{\textwidth}
		\begin{mathpar}
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n}\mapsto \texttt{NULL} \  \ast \ \texttt{pn->n->min}\mapsto \mathsf{n_1} \ \ast \ \texttt{pn->n->max}\mapsto\mathsf{n_2}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
		\left\{\exists \ \texttt{l r lk1 lk2}. 
		\begin{array}{c}
			\texttt{pn->n->t}\mapsto \texttt{(k, v, l, r)} \  \ast \ \texttt{pn->n->min}\mapsto \mathsf{n_1} \ \ast \ \texttt{pn->n->max}\mapsto\mathsf{n_2}  \ \ast \ 
			\\ \texttt{l} \mapsto (\texttt{NULL}, \texttt{lk1}, (\mathsf{n_1}, \mathsf{k})) \ \ast \ \texttt{r} \mapsto (\texttt{NULL}, \texttt{lk2}, (\mathsf{k}, \mathsf{n_2}))
		\end{array}
		\right\}
	}
	\end{mathpar}
	\caption{Specification of \texttt{insertOp} for the give-up template}
	\label{fig:insertOp_giveup}
\end{subfigure}
	\caption{Specification of \texttt{insertOp} for the lock-coupling and give-up templates}
	\label{fig:insertOp}
\end{figure}
